Non-word repetition among the Tsimane': A small-scale study

### 2019-10-11 manuscript.Rmd
first draft

\documentclass[english,,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Non-word repetition among the Tsimane': A small-scale study},
            pdfauthor={Alejandrina Cristia, Steven Levinson, \& Marisa Casillas},
            pdfkeywords={phonology, non-word repetition},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[shorthands=off,main=english]{babel}
\else
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\fi
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Non-word repetition among the Tsimane': A small-scale study}
    \author{Alejandrina Cristia\textsuperscript{1}, Steven Levinson\textsuperscript{2}, \& Marisa Casillas\textsuperscript{2}}
    \date{}

\shorttitle{NWR among the Tsimane'}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} LSCP, Département d’études cognitives, ENS, EHESS, CNRS, Université PSL\\\textsuperscript{2} MPI}
\keywords{phonology, non-word repetition\newline\indent Word count: xxx}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\authornote{

Correspondence concerning this article should be addressed to Alejandrina Cristia, 29, rue d'Ulm, 75005, Paris, France. E-mail: \href{mailto:alecristia@gmail.com}{\nolinkurl{alecristia@gmail.com}}}

\abstract{
ADD

}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\subsection{Introduction}\label{introduction}}

\begin{itemize}
\tightlist
\item
  many studies on phonological development in childhood
\item
  they show phonology continues developing as children learn more words and gain mastery of phonetic targets
\item
  one key task in this research in NWR
\item
  used for theory (eg what are the links between phonology, working memory, and lexicon?), and for applications (nwr as a diagnostic)
\item
  it has been used acros a wide array of languages, particularly in Europe
\item
  however, less is known about NWR development in non-Indo European languages
\item
  this study: NWR in a Yêly Dnyé, an isolate spoken in Rossel Island, PNG, with an unusually dense phonological inventory
\end{itemize}

@@

\hypertarget{intro-to-the-language}{%
\subsubsection{Intro to the language}\label{intro-to-the-language}}

\begin{itemize}
\tightlist
\item
  complexity in the vowel system
\item
  complexity in the consonant system
\item
  word shapes
\item
  typical word length
\item
  although not the focus of this paper, high use of suppletion in verbal paradigms, other features of language, see Levinson XXX for details
\end{itemize}

\hypertarget{intro-to-the-people}{%
\subsubsection{Intro to the people}\label{intro-to-the-people}}

\begin{itemize}
\tightlist
\item
  usually monolingual at home
\item
  schooling in English but it starts at age XX, so not relevant here
\item
  however, some use of English due to immigrants \& children of immigrants
\item
  children spend a lot of time with other children
\item
  most parents are subsistence farmers
\item
  parental education generally varies between XX and YY
\end{itemize}

\hypertarget{brief-review-of-nwr-for-our-purposes}{%
\subsubsection{Brief review of NWR for our purposes}\label{brief-review-of-nwr-for-our-purposes}}

\begin{itemize}
\item
  typical structure of NWR tasks: N of items
\item
  complexity varies widely across tasks, sometimes within tasks on purpose
\item
  some authors modulate structural complexity (nb syll, syllable structure), others familiarity via phonotactic probability
\item
  calculation of frequency in Yêli is challenging bc low resource language
\item
  so we only manipulated structural complexity, not probability
\item
  previous work seems to avoid difficult sounds
\item
  but we felt this was important to represent the language, so we also varied this factor
\item
  previous work shows even 2yo can do the task
\item
  but there are striking changes with age
\item
  inconsistent results RE effects of SES (including parental education) \& child sex
\item
  brief summary of inconsistent results SES
\item
  idem for sex
\end{itemize}

\hypertarget{research-questions-and-predictions}{%
\subsubsection{Research questions and predictions}\label{research-questions-and-predictions}}

\begin{itemize}
\tightlist
\item
  What is the accuracy (whole word, phoneme based, distance) overall?
\item
  How does this change as a function of item complexity (nb syll, syll complexity, sound complexity)?
\item
  How frequent are errors that result in real words? Is that a function of item complexity?
\item
  Is individual variation explainable by child age, sex, parental education?
\end{itemize}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Children are more accurate for mono-syllables than longer items
\item
  Similarly, we do not know of NWR research that manipulates the difficulty of the sounds that are included in the items, but word naming and other research suggests that children are more accurate when producing easy and/or typologically common sounds than difficult and/or typologically rare sounds
\item
  Children's accuracy increases with child age
\item
  Non-monolingual Yélî children are less accurate than monolingual ones when tested on the dominant language (we did not test any non-dominant language)
\item
  Previous NWR evidence on this is mixed, but general findings on language development suggest that children whose mothers are more educated are more accurate than children whose mothers are less educated
\item
  To our knowledge, there is no previous NWR work on this, but other research suggests that first-born children should outperfomr later-born children
\end{enumerate}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The length distribution in Yélî words is more balanced than that in English, and thus the performance decline for poly- versus mono-syllables may be less pronounced than that for English. \textbf{Check for work on European languages that may have looked into this}
\item
  The Yélî sound inventory is very large and compressed, with many similar sounds that are acoustic and articulatory neighbors. Therefore, this may constitute a pressure for children to have finer aduitory skills (and perhaps more precise articulations) than children speaking languages with a simpler inventory. \textbf{no work looking at consonants \& vowels? no work looking at nasal vowels in particular?}
\item
  We had no reservations that children's accuracy increases with child age for the Yélî community as well.
\item
  Anecdotally Yélî children grow up in close-knitted communities and thus may receive significant portions of their language input from non-kin (or at least from people other than their mothers, who tend to be the non-native speakers). If so, the difference between monolinguals and not monolinguals may be smaller than that found in other work. That said, one recent study shozs that most child-directed input in the first 2 years does come from the mother, so in so far as this input has a crucial formational role, then there may still be a performance gap between these two groups.
\item
  In the Rossel community, formal education plays an extremely minor role in ensuring individual's success, is not a good index of relative socio-economic status, and furthermore there is only a narrow range of variation in maternal educational attainment. This may lead to no or only very small advantages for children whose mothers are more educated, provided that the causal chain between maternal education and child language is via SES more broadly. However, if education directly boosts maternal verbal skills and the incidence of verbal behavior (as suggested by CITE), then we should still see a difference along this factor.
\item
  One main causal path between birth order and language development is via parental input (CITE). Given our arguments above for how mothers may not be as important among Rossel people than in other places, then the performance gap between first borns and later borns may be smaller.
\end{enumerate}

\hypertarget{pre-registration-and-planned-analyses}{%
\subsection{Pre-registration and planned analyses}\label{pre-registration-and-planned-analyses}}

@@

\begin{itemize}
\tightlist
\item
  The sample size is too small to have enough power to detect all of the relationships of interest
\item
  In fact, the sample size is too small to detect some of the known effects (see Table XX \textbf{add table with r/ds from previous work})
\item
  By virtue of this being a language-specific study, it is unclear that our method (including saliently the items we used) is comparable in precision to previous NWR studies
\item
  Analyses were designed and pre-registered by the same person who collected the data, who coded accuracy (albeit with a non-native ear) on the first 11 participants, and who segmented all children's production. Therefore, a key condition of blinding is not met
\end{itemize}

@@

\hypertarget{stimuli}{%
\subsection{Stimuli}\label{stimuli}}

@@

\begin{itemize}
\tightlist
\item
  the same 3 items were selected as practice items and used in all 40 elicitation sets
\item
  splits were done within each length group from the 2018 items (i.e., separately for 1, 2, 3, and 4-syllable items); and among onset groups for the difficult monosyllables generated in 2019 (i.e., all the monosyllables starting with tp were split into 2 sublists). Since some of these groups had an odd number of items, one of the sublists was slightly longer than the other (20 versus 23).
\item
  once the sublist split had been done, items were randomized such that all children heard first the 3 practice items in a fixed order (1, 2, and 4 syllables), a randomized version of their sublist selection of difficult onset items, and randomized versions of their 2\_syllables, then 3-syllables, and finally 4-syllable items.
\end{itemize}

@@

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

@@

Indeed, we visited four different hamlets once, and attempted to test all eligible childr en present at that time, to prevent the items \enquote{spreading} through hearsay. In the first village, we tested children in five different places, with some children being tested inside their house and others tested on the veranda of a house even if it was not their own. The complete list of places and the ways in which they met the desiderata mentioned above can be found in supplementary materials, under comments for each child (direct link xXX).

@@

\hypertarget{coding}{%
\subsection{Coding}\label{coding}}

There is an implicit accuracy coding occuring online as a function of whether the local informant asked for the item to be repeated or not. We will call this \enquote{online accuracy}, and it reflects a wholesale impression of whether the item was correctly or incorrectly repeated.

Additionally, the experimenter listened through all recordings and segmented out every child production. For the first 11 participants, she additionally made a judgment of whether the item was correctly or incorrectly repeated, and transcribed what she heard, which provides both an accuracy measure and a qualitative description of what children were actually saying in response to each stimulus. . We call this \enquote{non-native coding,} because this experimenter is not familiar with Yélî and has insufficient training on Yélî sounds, including common allophonic variants, not to mention not having some of the sounds in her native perceptual inventory.

Therefore, we sought additional information by asking a local informant to listen through each child production, paried with the auditory target the child had been provided with, and make a judgment of whether the item was correctly or incorrectly repeated. We additionally asked her to transcribe exactly what the child said, providing some examples of the types of errors children in general make (without making specific reference to Yélî sounds or the items in the elicitation sets). This \enquote{native coding} provides both accuracy and qualtiative desciptions of what the child said that are likely more reliable than those of the non-native coder.

\hypertarget{analyses}{%
\subsection{Analyses}\label{analyses}}

@@

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

@@

\begin{itemize}
\tightlist
\item
  child age
\item
  monoling
\item
  mat ed
\item
  birth order
\end{itemize}

\begin{verbatim}
##  [1] "X.3"         "ID"          "included"    "Age"         "DOB.ISO"    
##  [6] "DOB"         "Sex"         "birthOrder"  "familyID"    "monolingual"
## [11] "matEd"       "Cond"        "Date"        "Time"        "File"       
## [16] "fastcode"    "fullcode"    "Notes"       "Where"       "Village"    
## [21] "X"           "X.1"         "X.2"         "dob"         "test"       
## [26] "age.exact"
\end{verbatim}

\begin{verbatim}
##     ID score.online
## 1  c70    0.7307692
## 2  c71    0.5384615
## 3  c72    0.6086957
## 4  c73    0.8461538
## 5  c74    0.9090909
## 6  c76    0.7307692
## 7  c77    0.9565217
## 8  c78    0.8461538
## 9  c79    0.7692308
## 10 c80    0.8260870
## 11 c81    0.5652174
## 12 c82    0.5000000
\end{verbatim}

\includegraphics{manuscript_files/figure-latex/cars-1.pdf} \includegraphics{manuscript_files/figure-latex/cars-2.pdf} \includegraphics{manuscript_files/figure-latex/cars-3.pdf}

\hypertarget{discussion}{%
\subsection{Discussion}\label{discussion}}

@@

\hypertarget{acknowledgments}{%
\subsection{Acknowledgments}\label{acknowledgments}}

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\end{document}

>>>>

---
title: "Non-word repetition among the Tsimane': A small-scale study"
shorttitle        : "NWR among the Tsimane'"

author: 
  - name          : "Alejandrina Cristia"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "29, rue d'Ulm, 75005, Paris, France"
    email         : "alecristia@gmail.com"
  - name          : "Steven Levinson"
    affiliation   : "2"
  - name          : "Marisa Casillas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "LSCP, Département d’études cognitives, ENS, EHESS, CNRS, Université PSL"
  - id            : "2"
    institution   : "MPI"

author_note: >

abstract: >    
    ADD

keywords          : "phonology, non-word repetition"
wordcount         : "xxx"

bibliography      : ["nwrbib.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : no

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf

---

```{r setup, include=FALSE}
#Sys.setlocale("LC_CTYPE", "en_US_POSIX.UTF-8")
#Sys.setlocale("LANG", "en_US_POSIX.UTF-8")
Sys.setlocale(category = "LC_ALL", locale = "en_SE.utf8")

knitr::opts_chunk$set(warning = FALSE, message = FALSE, cache = FALSE, fig.pos = "T")
require("papaja")

```

## Introduction

- many studies on phonological development in childhood
- they show phonology continues developing as children learn more words and gain mastery of phonetic targets
- one key task in this research in NWR
- used for theory (eg what are the links between phonology, working memory, and lexicon?), and for applications (nwr as a diagnostic)
- it has been used acros a wide array of languages, particularly in Europe
- however, less is known about NWR development in non-Indo European languages
- this study: NWR in a Yêly Dnyé, an isolate spoken in Rossel Island, PNG, with an unusually dense phonological inventory

@@

### Intro to the language

- complexity in the vowel system
- complexity in the consonant system
- word shapes
- typical word length
- although not the focus of this paper, high use of suppletion in verbal paradigms, other features of language, see Levinson XXX for details

### Intro to the people

- usually monolingual at home
- schooling in English but it starts at age XX, so not relevant here
- however, some use of English due to immigrants & children of immigrants
- children spend a lot of time with other children
- most parents are subsistence farmers
- parental education generally varies between XX and YY

### Brief review of NWR for our purposes

- typical structure of NWR tasks: N of items
- complexity varies widely across tasks, sometimes within tasks on purpose
- some authors modulate structural complexity (nb syll, syllable structure), others familiarity via phonotactic probability
- calculation of frequency in Yêli is challenging bc low resource language
- so we only manipulated structural complexity, not probability
- previous work seems to avoid difficult sounds
- but we felt this was important to represent the language, so we also varied this factor

- previous work shows even 2yo can do the task
- but there are striking changes with age
- inconsistent results RE effects of SES (including parental education) & child sex

- brief summary of inconsistent results SES

- idem for sex

### Research questions and predictions

- What is the accuracy (whole word, phoneme based, distance) overall?
- How does this change as a function of item complexity (nb syll, syll complexity, sound complexity)?
- How frequent are errors that result in real words? Is that a function of item complexity?
- Is individual variation explainable by child age, sex, parental education?

@@

1. Children are more accurate for mono-syllables than longer items
2. Similarly, we do not know of NWR research that manipulates the difficulty of the sounds that are included in the items, but word naming and other research suggests that children are more accurate when producing easy and/or typologically common sounds than difficult and/or typologically rare sounds
3. Children's accuracy increases with child age
4. Non-monolingual Yélî children are less accurate than monolingual ones when tested on the dominant language (we did not test any non-dominant language)
5. Previous NWR evidence on this is mixed, but general findings on language development suggest that children whose mothers are more educated are more accurate than children whose mothers are less educated
6. To our knowledge, there is no previous NWR work on this, but other research suggests that first-born children should outperfomr later-born children

@@

1. The length distribution in Yélî words is more balanced than that in English, and thus the performance decline for poly- versus mono-syllables may be less pronounced than that for English. **Check for work on European languages that may have looked into this**
2. The Yélî sound inventory is very large and compressed, with many similar sounds that are acoustic and articulatory neighbors. Therefore, this may constitute a pressure for children to have finer aduitory skills (and perhaps more precise articulations) than children speaking languages with a simpler inventory. **no work looking at consonants & vowels? no work looking at nasal vowels in particular?**
3. We had no reservations that children's accuracy increases with child age for the Yélî community as well.
4. Anecdotally Yélî children grow up in close-knitted communities and thus may receive significant portions of their language input from non-kin (or at least from people other than their mothers, who tend to be the non-native speakers). If so, the difference between monolinguals and not monolinguals may be smaller than that found in other work. That said, one recent study shozs that most child-directed input in the first 2 years does come from the mother, so in so far as this input has a crucial formational role, then there may still be a performance gap between these two groups.
5. In the Rossel community, formal education plays an extremely minor role in ensuring individual's success, is not a good index of relative socio-economic status, and furthermore there is only a narrow range of variation in maternal educational attainment. This may lead to no or only very small advantages for children whose mothers are more educated, provided that the causal chain between maternal education and child language is via SES more broadly. However, if education directly boosts maternal verbal skills and the incidence of verbal behavior (as suggested by CITE), then we should still see a difference along this factor.
6. One main causal path between birth order and language development is via parental input (CITE). Given our arguments above for how mothers may not be as important among Rossel people than in other places, then the performance gap between first borns and later borns may be smaller.

## Pre-registration and planned analyses

@@

- The sample size is too small to have enough power to detect all of the relationships of interest
- In fact, the sample size is too small to detect some of the known effects (see Table XX **add table with r/ds from previous work**)
- By virtue of this being a language-specific study, it is unclear that our method (including saliently the items we used) is comparable in precision to previous NWR studies
- Analyses were designed and pre-registered by the same person who collected the data, who coded accuracy (albeit with a non-native ear) on the first 11 participants, and who segmented all children's production. Therefore, a key condition of blinding is not met

@@

## Stimuli

@@

- the same 3 items were selected as practice items and used in all 40 elicitation sets
- splits were done within each length group from the 2018 items (i.e., separately for 1, 2, 3, and 4-syllable items); and among onset groups for the difficult monosyllables generated in 2019 (i.e., all the monosyllables starting with tp were split into 2 sublists). Since some of these groups had an odd number of items, one of the sublists was slightly longer than the other (20 versus 23).
- once the sublist split had been done, items were randomized such that all children heard first the 3 practice items in a fixed order (1, 2, and 4 syllables), a randomized version of their sublist selection of difficult onset items, and randomized versions of their 2_syllables, then 3-syllables, and finally 4-syllable items.

@@

## Procedure

@@

Indeed, we visited four different hamlets once, and attempted to test all eligible childr en present at that time, to prevent the items 'spreading' through hearsay. In the first village, we tested children in five different places, with some children being tested inside their house and others tested on the veranda of a house even if it was not their own. The complete list of places and the ways in which they met the desiderata mentioned above can be found in supplementary materials, under comments for each child (direct link xXX).

@@

## Coding

There is an implicit accuracy coding occuring online as a function of whether the local informant asked for the item to be repeated or not. We will call this "online accuracy", and it reflects a wholesale impression of whether the item was correctly or incorrectly repeated.

Additionally, the experimenter listened through all recordings and segmented out every child production. For the first 11 participants, she additionally made a judgment of whether the item was correctly or incorrectly repeated, and transcribed what she heard, which provides both an accuracy measure and a qualitative description of what children were actually saying in response to each stimulus. . We call this "non-native coding," because this experimenter is not familiar with Yélî and has insufficient training on Yélî sounds, including common allophonic variants, not to mention not having some of the sounds in her native perceptual inventory.

Therefore, we sought additional information by asking a local informant to listen through each child production, paried with the auditory target the child had been provided with, and make a judgment of whether the item was correctly or incorrectly repeated. We additionally asked her to transcribe exactly what the child said, providing some examples of the types of errors children in general make (without making specific reference to Yélî sounds or the items in the elicitation sets). This "native coding" provides both accuracy and qualtiative desciptions of what the child said that are likely more reliable than those of the non-native coder.

## Analyses

@@

## Participants

@@

- child age
- monoling
- mat ed
- birth order

```{r cars}
# read.csv("NWR-test-log_FINAL.csv",header=T,sep=";")->fulldemo
# fulldemo=fulldemo[,-2] #remove children's names
# fulldemo$dob=as.Date(as.character(fulldemo$DOB.ISO),format="%Y%m%d")
# fulldemo$test=as.Date(as.character(fulldemo$Date),format="%Y%m%d")
# fulldemo$age.exact=as.numeric(difftime(fulldemo$test,fulldemo$dob,unit="weeks"))/52.25
# fulldemo$Age=as.numeric(as.character(fulldemo$Age))
# plot(fulldemo$Age~fulldemo$age.exact)     
# write.csv(fulldemo,"nwr-demo.csv")

read.csv("NWR-demo.csv",header=T)->demo
colnames(demo)
read.table("log2.txt",header=T,sep="\t")->x
x$rep=gsub(".wav","",gsub(".*_","",x$out),fixed=T)
x[order(x$out),]->x
x$cor.online=1
for(i in 1:dim(x)[1]) if(x$rep[i]>1) x$cor.online[i-1]<-0

subset(x,rep=="1")->x
aggregate(x$cor.online,by=list(x$child),mean)->onl
colnames(onl)<-c("ID","score.online")

print(onl)

aggregate(x$corr,by=list(x$child),mean)->ms
colnames(ms)<-c("ID","score")
merge(ms,onl)->ms
merge(ms,demo)->scores
scores$Age=as.numeric(as.character(scores$Age))
scores$Age[is.na(scores$Age)]<-15
plot(scores$score*100~scores$Age,pch=20,xlab="Age (years)",ylab="% Correct")
abline(lm(scores$score*100~scores$Age))
plot(scores$score~scores$monolingual)
points(scores$score~as.numeric(scores$monolingual),pch=20)

plot(ms$score.online~ms$score)

```

## Discussion

@@

## Acknowledgments

@@

# References

@@
